\documentclass[a4paper, english]{scrartcl}

\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{booktabs}
\usepackage{microtype}
% TODO Fix title below
\usepackage[pdftitle = {TODO TITLE HERE}, colorlinks = true, urlcolor = blue, linkcolor = blue, citecolor = blue]{hyperref}

% TODO Fix title here
\title{Optical Character Recognition}
\subtitle{Subtitle here \ldots}
% TODO Add names here
\date{DATE HERE, 2017}
\author{Irvin,~Duane \\ \texttt{duane@student.chalmers.se}
  \and Karlsson,~Pontus \\ \texttt{ponkarls@student.chalmers.se}
  \and Holm,~Jesper \\ \texttt{~holmje@student.chalmers.se}
  \and Subramanian,~Aditya \\ \texttt{email@student.chalmers.se}
}

\begin{document}

\clearpage\maketitle
\thispagestyle{empty}

\pagebreak

\setcounter{page}{1}
\hypersetup{linkcolor=black}
\tableofcontents

\pagebreak

\section{Introduction}
\subsection{Background}
This project being performed on behalf of Cybercom,
a Nordic IT consulting company with multiple offices throughout the world.
This project will be done in cooperation with the Cybercom Gothenburg office.
The purpose of the project is to design a system capable of recognizing text 
in an image and convert it into text or audio output. 
The primary project description is kept as simple as possible. 
However the intention is that if the primary functionality and tests are 
finished the project scope and functionality can be extended depending on 
time and resource constraints. 
In the future the project could be expanded into a hardware implementation 
to be used by vision impaired people with text to speech functionality.
\subsection{Purpose}
The primary purpose of this project is to create a character recognition
system using pre-existing libraries such as OpenCV. 
A secondary purpose is for Cybercom to build a connection with students 
who may become future engineers. 
\subsection{Vision}
The goal of this project is to develop a software that can recognise 
characters on a image file. 
The image is suppose to be taken with a laptop camera or something equivalent.
And the software should be running on an Linux or Android platform. 
For starters we are going to aim at single character recognition.
Once the character is recognised it should be printed to a text file.
If there is time, there will be further development on word recognition and
to translate words to voice.

Features below are denoted with RF for required features and OF for optional
features.
  \noindent\begin{tabularx}{\linewidth}{X p{0.75\linewidth}}
  \toprule
    \textbf{Feature} & \textbf{Description} \\
  \midrule
  RF-1 &
    From an image, recognize characters with an accuracy of at least 75\%. Preferably better than 80\%. \\
  RF-2 &
    Turn text into English speech output. \\
  RF-3 &
    User interface that implements RF-1 and RF-2. \\
  \bottomrule
  \end{tabularx}
\subsection{Scope}

\section{Method}
% TODO Fix title below
\subsection{TODO\{title\} Framework for the way we work yao}
\subsection{Testing}

\section{Technical Background}

\section{Implementation}
\subsection{Use cases}
\subsection{UML/Modules}
\subsection{Tests}

\section{Result}
\subsection{Did we achieve our goals}

\section{Discussion}

\pagebreak
% Ask me how to properly insert references // Duane
\bibliography{references}
\bibliographystyle{ieeetr}

\end{document}
